Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-07-07 demystify.tex
updates

\paragraph{GRE} While a few schools still require taking the GRE (e.g., UCF), most good CS PhD programs in the US \textbf{no longer} require it.

Thus, if you haven't taken the GRE or have bad scores, then don't waste time (re)taking it. It does not help much!

@@

\begin{commentbox}[Vu:]
  If you got recruited an offered an RA by a prof., you will likely get admitted.  For example, if a prof., even if not in PhD adcom, wants to fund you, adcom will respect that decision and admit you (unless your application has many red flags).
\end{commentbox}

>>>>

\paragraph{GRE} While a few schools still require taking the GRE (e.g., UCF), most good CS PhD programs in the US \textbf{no longer} require it. Thus, if you haven't taken the GRE or have bad scores, then don't waste time (re)taking it. It does not help much!

@@

\begin{commentbox}[Vu:]
  If you got recruited and offered an RA by a prof., you will likely get admitted.  For example, if a prof., even if not in PhD adcom, wants to fund you, adcom will likely respect that decision and admit you.
\end{commentbox}
